\documentclass{dcthesis}
\usepackage{listings}
% This version of the thesis template has been updated for the February 2017 thesis guidelines provided by the School of Graduate and Advanced Studies by David Freund and Daryl DeFord. It was later further updated by Marek Svoboda on 12/25/2021 to conform to the latest update in the guidelines from 10/05/2021.

% Some good options are draft and singlespacing, for drafts, and *final*, for the final cut, and noheadings, for a printout without headings. You can also use the copyright option to add a copyright.  Note: final will enforce a bunch of different options, like oneside, 12pt and doublespacing, as well as make the margins correct. Draft has larger margins and is appropriate for twosided printing.   


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%    IMPORTANT     %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  Because dvips doesn't know/care about the page size of the dvi file its working on, and because its so important that the margins of your thesis are correct you have to make sure that you are using the command dvi -t letter *thesisnamehere*
%  If you are using a terminal this is straightforward, but if you are using a tex editing program it make take a little bit of searching before you figure out how to make this work.
%  Alternatively, you might consider compiling using pdflatex, which compiles straight to a PDF and doesn't have this problem.  

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Some Defaults
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\committee[F. Jon Kull, Ph.D.]{}{}{}{}
\School{Guarini School of Graduate and Advanced Studies}{Dartmouth College}{Hanover, New Hampshire}
\degree{Doctor of Philosophy}
\field{Mathematical Modeling Optics Astrophysics and Computation}
% List of approved fields:
% - Optics
% - Laser Science
% - Mathematical Modeling
% - Astrophysics
% - Cognitive Neuroscience
% - Computer Science
% - Digital Musics
% - Earth Sciences
% - Ecology, Evolution, Environment and Society
% - Engineering Sciences [TITLE PAGE DIFFERS - SEE GUIDELINES]
% - Experimental and Molecular Medicine
% - Health Policy and Clinical Practice
% - Integrative Neuroscience
% - Master of Arts in Liberal Studies [TITLE PAGE DIFFERS - SEE GUIDELINES]
% - Mathematics
% - Microbiology and Immunology
% - Molecular and Systems Biology
% - Physics and Astronomy
% - Psychological and Brain Sciences
% - Quantitative Biomedical Sciences

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Additional Packages (add as desired)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,amssymb,amsthm}

%\usepackage{mkindex} %Uncomment if you would like to have an index. Compiling with an index takes more work than compiling without one. You will have to look up how to use the index package.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Formatting
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Change or add to as desired. 
%  These two commands make the first enumerations look like (a) and the second level like (i).  
\renewcommand{\labelenumi}{(\alph{enumi})}
\renewcommand{\labelenumii}{(\roman{enumii})}
%  These commands make the section headings Boldface and not all caps. It also removes the chapter numbers  
\renewcommand{\chaptermark}[1]{\markboth{{\sc #1}}{{\sc #1}}}
\renewcommand{\sectionmark}[1]{\markright{{\sc \thesection\ #1}}}
%  These commands have lowercase headings with chapter numbers. 
%\renewcommand{\chaptermark}[1]{markboth{#1}{}}
%\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}} 
		
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Theorem Declarations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A basic set of theorem declarations.  Add or remove as desired. 
\newtheorem{prop}{Proposition}[chapter]
\newtheorem{theorem}[prop]{Theorem}
\newtheorem{lemma}[prop]{Lemma}
\newtheorem{corr}[prop]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[prop]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[prop]{Remark}
\newtheorem{example}[prop]{Example}
\newtheorem*{claim}{Claim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Indicies
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%This is for an index.  More work is neede for a notation index
%\makeindex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Macros
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Add your math macros here

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title Page Information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Your personal info goes here!
\title{My Education and Experience Compilation: A Summary of being angry enough to write a thesis dissertation on math modeling and optics since I could not have funding after this and I'm tired of being in remedial or elementary math courses}
\author{Hannah Gallagher}
\date{December 2021}
\field{Mathematical Modeling/ Astrophysics/ Optical and Laser Sciences/ Computer Science/ Whatever I do}
\degree{Doctor of Philosophy}
%As an optional arguement to \committee you can specify the dean of graduate studies.
\committee{LGF}{The Mustache}{The Big Cheese}{Totally Real Subfield}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Front end of thesis
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\frontmatter

\newgeometry{left=1.5in,top=1in,bottom=1in,right=1in}
\maketitle
\restoregeometry

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%NOTE:  Must be less than 350 words.  
\chapter*{Abstract}
%This is so the abstract appears in the ToC
\addcontentsline{toc}{section}{Abstract}
The study of light is a fascinating field. Here we delve into the mathematical models and framework of this phenomenon. Not entirely sure what to write here yet... I would probably need to do some derivations for this right? Idk it all started with Snell's law and now I'm here saying I understand optics and astrophysics statistics computation things...because idk I'm a woman and if I'm not a prodigy now then everyone will ignore me and I'll have to be someone's wife instead of just someone with no prizes to give conferences in France. The men I hang around talk to me like I'm stupid or in a lower rank so I'd like to dissertate before them and before I lose my funding or go into debt over dumb things like a couch or children thanks. Most of this needs to be taken care of before I have to be reminded of my karma. I guess the research I usually do is optics, astrophysics, and statistics with python and Matlab. 

\chapter*{Preface}
\addcontentsline{toc}{section}{Preface}
I do love everyone, but I kind of hate them right now so that I can make sure to do this thing before I turn 26 and honestly before new years and before I have to deal with finding funding and everything...or more debt because I've already suffered enough...a dissertation is nothing comparatively.  

Thank you to Austin for supporting me. \\\
Thank you to my parents for believing in me when no one else did. Thank you to Brennan for noticing the absurdity of the situation the encouragement helped immensely when I was down on my luck. \\ Thank you Nicole for 
Thank you Jared and Anjali for not getting too annoyed with me when I was clueless about research. 
Thank you Dr. Campaneli for being patient with me when I was struggling. 
Thank you to the UR Optics department and my colleagues there and being life long friends even in the hardest times. \\ 
Thank you to the Math department at RIT for supporting me and managing me when I had my head in the clouds too often. 

It only took a global pandemic and my dad's cancer to get me to write this. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Table of Contents
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tableofcontents

%Add a list of tables
%\listoftables

%Add a list of figures
%\listoffigures

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Main Portion of Thesis
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mainmatter
I deserve an optics math modeling whatever phD. I transferred schools so my learning was off base and I had to do a lot on my own since I was 21 and then the pandemic happened so I got mad enough to basically dissertate here and if anyone wants to claim me you know where I am. Next moves I may continue astro...I may continue Optics. I may get a random job to fund my research per usual at this point. I would like advice and aid, but I'd like to know that I wrote this well before 26 before I start getting shamed for not having a husband house or children...oh wait. Isn't the world amazing (respectfully) fuck all of you I'll continue to make your lives a living hell because at this point I have skill so you can't put me in the kitchen that's where I keep my quantum textbooks and listen to lectures while my imaginary cook husband does all of that for me...sounds crazy and spiteful...please omit.  
%%%%%%%%%%%%%%%%%%%%%%%%%
%%  YOUR THESIS HERE!  %%
%%%%%%%%%%%%%%%%%%%%%%%%%
\include{Chapters/BootstrappingMyself}
\include{Chapters/-2StatementofPurpose}
\include{Chapters/-1NotesNegative}

\include{Chapters/Outline}
\include{Chapters/chapter1}
\include{Chapters/chapter2optics}
\include{Chapters/chapter3BitterKarmaRIT}
\include{Chapters/chapter4astrotonotbebored}
\include{Chapters/chapter5pandemicriftligojoy}
\include{Chapters/Chapter6Math}
\include{Chapters/Chapter7ProofsDummies}
\include{Chapters/Chapter8WhateverIdidwithRIFT}
\include{Chapters/Chapter9}
\include{Chapters/Chapter10Readingjobapplications}
\include{Chapters/Chapter11}
\include{Chapters/Chapter12}
\include{Chapters/chapter13}
\include{Chapters/Chapter14Aquisitions}
\include{Chapters/chapter15}
\include{Chapters/Chapter16Manuelawillbemostpleased}
\include{Chapters/Chapter17MathModelingOpticsThesis}
\include{Chapters/Chapter18MHD}
\include{Chapters/Chapter19}
\include{Chapters/Chapter20}
\include{Chapters/Chapter21}
\include{Chapters/notesonrealanalysis}

\appendix
\include{appendixA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Backend of thesis (references and the like)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\backmatter

%Add your bibliography filename and uncomment these lines
%\bibliographystyle{amsplain}
%\addcontentsline{toc}{chapter}{References}
%\bibliography{}
%\markboth{{\sffamily\sc Bibliography}}{}


\begin{thebibliography}{}
\bibitem{Workplace}
Agarwal, Dr. Pragya. “How Does Lighting Affect Mental Health In The Workplace.” Forbes, Forbes Magazine, 31 Dec. 2018, www.forbes.com/sites/pragyaagarwaleurope/2018/12/31/how-does-lighting-affect-mental-health-in-the-workplace/?sh=6d56c91e4ccd. 

\bibitem{Eye Circulation}
Bell, Michael & Ross, David & Bautista, Maurino & Shahmohamad, Hossein & Langner, Andreas & Hamilton, John & Lahnovych, Carrie & Thurston, George. (2017). Statistical-thermodynamic model for light scattering from eye lens protein mixtures. The Journal of Chemical Physics. 146. 055101. 10.1063/1.4974155. 

\bibitem{Heart}
Bhat, Naresh. “Health Care: Data Set on Heart Attack Possibility.” Kaggle, 25 June 2020, www.kaggle.com/nareshbhat/health-care-data-set-on-heart-attack-possibility. 

\bibitem{CDC}
CDC. “Certain Medical Conditions and Risk for Severe COVID-19 Illness.” Centers for Disease Control and Prevention, Centers for Disease Control and Prevention, 1 Dec. 2020, www.cdc.gov/coronavirus/2019-ncov/need-extra-precautions/people-with-medical-conditions.html. 

\bibitem{Light Pollution}
Chen, X., and W. D. Nordhaus. “Using Luminosity Data as a Proxy for Economic Statistics.” Proceedings of the National Academy of Sciences, vol. 108, no. 21, 2011, pp. 8589–8594., doi:10.1073/pnas.1017031108. 

\bibitem{Eye Diseases}
Datacrunch. “Prevalence of Vision Problems in the U.S. - Dataset by Datacrunch.” Data.world, 11 May 2017, data.world/datacrunch/prevalence-of-vision-problems-in-the-u-s. 

\bibitem{Sleep and Blue Light} Gradisar, Michael, et al. “The Sleep and Technology Use of Americans: Findings from the National Sleep Foundation's 2011 Sleep in America Poll.” Journal of Clinical Sleep Medicine, vol. 09, no. 12, 2013, pp. 1291–1299., doi:10.5664/jcsm.3272. 

\bibitem{Circadian Rhythm}Moller-Levet, C. S., et al. “Effects of Insufficient Sleep on Circadian Rhythmicity and Expression Amplitude of the Human Blood Transcriptome.” Proceedings of the National Academy of Sciences, vol. 110, no. 12, 2013, doi:10.1073/pnas.1217154110. 

\bibitem{Survey}
Open Sourcing Mental Illness, LTD. “Mental Health in Tech Survey.” Kaggle, 3 Nov. 2016, www.kaggle.com/osmi/mental-health-in-tech-survey. 


\bibitem{Light Polution and Wealth}
Proville, Jeremy & Zavala-Araiza, Daniel & Wagner, Gernot. (2017). Night-time lights: A global, long term look at links to socio-economic trends. PLOS ONE. 12. e0174610. 10.1371/journal.pone.0174610. 

\bibitem{Patient}
Joseph, Anjali. “Impact of Light on Outcomes in Healthcare Settings.” Impact of Light on Outcomes in Healthcare Settings | The Center for Health Design, The Center for Health Design, 2006, www.healthdesign.org/chd/research/impact-light-outcomes-healthcare-settings. 

\bibitem{Lighting Quality}
Kralikova, Ruzena & Piňosová, Miriama & Hricová, Beata. (2016). Lighting Quality and its Effects on Productivity and Human Healts. International Journal of Interdisciplinary in Theory and Practice ISSN 2344-2409. 10. 8-12. 

\bibitem{Recovery}
Walch JM, Rabin BS, Day R, Williams JN, Choi K, Kang JD. The effect of sunlight on postoperative analgesic medication use: a prospective study of patients undergoing spinal surgery. Psychosom Med. 2005 Jan-Feb;67(1):156-63. doi: 10.1097/01.psy.0000149258.42508.70. PMID: 15673638.


https://physionet.org/content/mmash/1.0.0/



\end{thebibliography}


%Uncomment if you want an index
%\printindex

\end{document}