\chapter{Initial discoveries}

(This is where I talk about my initial ideas and interests when I was younger and all the Flubber scientist things.) Astronomy projects with my dad and everything. 
I learned about the optics program in my AP physics program. This is where I was introduced to the concepts of the angle of incidence and Snell's Law. 

\section[Shorter Title]{Optics Program Cult of Friends}

At UR I audited OPT 241, 261, and 287 in '19. This is where I was introduced to the idea of expanding models of how light travels and how one can simulate its properties. I kept in network with any of my classmates and observed the phenomenon they were interested in or assigned. At the end of the day it was some undergrads running around with laser pointers. Photon cup I was basically a cheerleader because they thought I knew less.  

\subsection{Well I understand it now since I read osa/optica papers every day and looked up what I didn't know}

I own two whiteboards in my apartment and should be respected as such. At first it was a motivational thing when I was depressed to keep on with everything...just to be patient sort of thing and that if I read enough of the papers and publishing I would understand enough to do it myself. 

\subsubsection{Subsubsections, the final formatted heading}

Now I actually have skill in these subjects out of the pressure to perform and honestly my network is full of men so I need to put them in their place. 

\section{A Second Section}

I studied astrophysics because my ex broke my heart. As the TSwizzle song goes...I bet you think about me. "Oh my god she's insane she wrote a astrophysics/optics thesis about me. I bet you think about me." That's how it goes right?